---
title: "Predicting CNX Nifty Index for 14th March,2016"
author: "Shubhankar Gupta"
date: "March 8, 2016"
output: 
  html_document: 
    keep_md: yes
---

I have used an ARIMA model to do the time series analysis and predicting the required value.

Loading the data from Yahoo finance for CNX Nifty from 3rd September,2015 to 4th March,2016
```{r}
suppressWarnings(suppressMessages(library(quantmod)))
from.dat = as.Date("09/03/15", format= "%m/%d/%y")
to.dat = as.Date("03/04/16", format= "%m/%d/%y")
suppressWarnings(suppressMessages(getSymbols("^NSEI",src = "yahoo", from= from.dat, to= to.dat)))
head(NSEI,2)
```

Using Only Closing Value for our Analysis.
```{r}
nseiclose = Cl(NSEI)
```

Converting NSEI into time series class. I further used a difference form of the time series in order to obtain the autocorrelation.  
```{r}
ts1 = ts(nseiclose,frequency = 1)
plot(ts1)
ts1diff = diff(ts1,differences = 2)
plot.ts(ts1diff)
```

I plotted the autocorrelation and partial autocorrelation funtion.
```{r}
acf(ts1diff,lag.max = 20)
pacf(ts1diff,lag.max = 20)
```
Since the correlogram tails off to zero after lag 3, and the partial correlogram is zero after lag 2, the following ARMA models are possible for the time series:

- an ARMA(2,0) model, since the partial autocorrelogram is zero after lag 2, and the correlogram tails off to zero after lag 3, and the partial correlogram is zero after lag 2.
- an ARMA(0,1) model, since the autocorrelogram is zero after lag 1, and the partial correlogram tails off to zero.
The ARMA(2,0) model has 2 parameters, the ARMA(0,1) model has 1 parameters. Using principle of parsimony we select ARMA(0,1) and thus ARIMA(0,2,1), since d=2.  
```{r}
suppressMessages(suppressWarnings(library(forecast)))
fcastarima = arima(ts1,order = c(0,2,1))
fcastarimaforecast = forecast.Arima(fcastarima,h=5)
plot(fcastarimaforecast)
fcastarimaforecast
```
Last forecast corresponds to the prediction for 14th March.